---
title: "p8105_hw5_csl2209"
author: "Casandra Laney"
date: "2025-11-14"
output: github_document
---

```{r include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Make a function
```{r}
bday_sim = function(n_room) {
  
  birthdays = sample(1:365, n_room, replace = TRUE)

  repeated_bday = length(unique(birthdays)) < n_room

  repeated_bday
}

```

check it works 
```{r}
bday_sim(5)
```

Run function 10000 times for each group size between 2 and 50
```{r}
bday_sim_results =
  expand_grid(
    bdays = 2:50,
    iter = 1:10000
  ) |>
  mutate(
    result = map_lgl(bdays, bday_sim)
  ) |>
  group_by(
    bdays
  ) |>
  summarize(
    prob_repeat = mean(result)
  )
```


Make a plot
```{r}
bday_sim_results |>
  ggplot(aes(x = bdays, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

Comment on your results:

## Problem 2

Write the function
```{r}
one_samp_t_sim = function(mu_hat) {
  
  one_samp = rnorm(30, mean = mu_hat, 5)
  
  one_samp_test = t.test(one_samp, mu = 0)
  
  broom::tidy(one_samp_test)
}
```

test it

```{r}
one_samp_t_sim(5)
```

Run function 5000 times for each group size between 1 and 6
```{r}
one_samp_sim_results =
  expand_grid(
    mu_values = 1:6,
    iter = 1:5000
  ) |>
  rowwise() |>
  mutate(
    result = map(mu_values, one_samp_t_sim)
  ) |>
  unnest(result)
```


Make a plot showing the proportion of time null was rejected
```{r}

one_samp_sim_results |>
  group_by(mu_values) |>
  summarize(power = mean(p.value < 0.05)) |>
  ggplot(aes(x = mu_values, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Power Curve of One-Sample t-Test",
    x = "True Value of μ",
    y = "Proportion of Null Rejected (Power)"
  )
```


Plot of avg estimate vs true value 
```{r}
one_samp_sim_results |>
  group_by(mu_values) |>
  summarize(avg_estimate = mean(estimate)) |>
  ggplot(aes(x = mu_values, y = avg_estimate)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Average Sample Mean vs True Mean",
    x = "True μ",
    y = "Average Estimated Mean"
  )
```


Plot of avg estimate in rejected nulls 
```{r}
one_samp_sim_results |>
  filter(p.value < 0.05) |> 
  group_by(mu_values) |>
  summarize(avg_rejected = mean(estimate)) |>
  ggplot(aes(x = mu_values, y = avg_rejected)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Average Estimate in Rejected Null Simulations",
    x = "True μ",
    y = "Average Estimated Mean (Only When Null Rejected)"
  )
```


## Problem 3

```{r}
homicide_data = read_csv("data/homicide-data.csv")
```


The dataset 'homicide-data' contains 12 variables of criminal homicide data collected in 50 of the largest American cities. 

Important variables include:

* 'reported_date': the date the case was reported

* 'victim_last': the last name of the victim

* 'victim_first': the first name of the victim

* 'victim_race': the race of the victim

* 'victim_age': the age of the victim


Summarize within cities to obtain the total number of homicides and the number of unsolved homicides

```{r}
city_homicides = 
  homicide_data |>
  mutate(
    city_state = str_c(city, state, sep = ", ")) |>
  group_by(city_state) |>
  summarize(
    total_homicides = n(),
    unsolved_homicides = 
      sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) 

city_homicides
```

Use the prop.test function to estimate proportion of homicides for Baltimore

```{r}
baltimore = 
  city_homicides |>
  filter(city_state == "Baltimore, MD")

prop.test(
  x = baltimore$unsolved_homicides,
  n = baltimore$total_homicides
) |> 
  broom::tidy()

baltimore
```


Run prop.test for each city
```{r}
city_prop_tests =
  city_homicides |>
  mutate(
    prop_test = 
      map2(unsolved_homicides, total_homicides, \(x, n) prop.test(x, n)
    ),
    tidied = map(prop_test, broom::tidy)
  ) |>
  select(city_state, tidied) |>
  unnest(tidied)


```

Plot of estimates & CIs for each city
```{r}
city_prop_tests |>
  mutate(city_state = fct_reorder(city_state, estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Estimated Proportion (95% CI)"
  )

```

